Preprocessing overview

### 2021-01-18 inst/examples/overview.Rmd
ok

# Preprocessing summary

The data spanning years `r min(na.omit(df$publication_year))`-`r max(na.omit(df$publication_year))` has been included and contains `r nrow(df.preprocessed)` documents (also other filter may apply depending on the data collection, see the source code for details.

@@

>>>>

# Preprocessing summary: Fennica

The data spanning years `r min(na.omit(df$publication_year))`-`r max(na.omit(df$publication_year))` has been included and contains `r nrow(df.preprocessed)` documents (additional filters may apply depending on the analysis, see the source code for details).

@@

Fields of special interest. Real success percentage (proportion of successful conversions compared to non-NA entries in the original data):

```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
select.fields <- c("author","publication_place","publication_country","publication_year",
                     "publication_year_from","publication_year_till","corporate","area","pagecount",
		     "gatherings","width","height","publisher","self_published")

dfs <- df

success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))

original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place,
                    publication_time, corporate, physical_extent, physical_dimension, publisher, author_name),
		      2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))

# Compare the number of non-NA entries in preprocessed data to number
# of non-NA entries in the original data:
real.success <- c()
real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
real.success[["publication_country"]] <- success$publication_country/original.nonNA$publication_place
real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
real.success[["area"]] <- success$area/original.nonNA$physical_dimension
real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
real.success[["author"]] <- success$author/original.nonNA$author
# real.success[["paper"]] <- success$paper/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
real.success <- unlist(real.success)
par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
```
